New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/article.tex
kaboom

\begin{remark}
\(SE_+\) and \(S\) have the same asymptotic growth rate.
\end{remark}

\subsection{Inequaties on SE_+}

The main result on \(SE_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(SE_+\).

\begin{theorem}
Let \(n, k \in \mathbb{N}^*\), we have \\
\[ S(n+k) \geq SE_+(k+1)S(n) \]
\end{theorem}

Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperlink{SAT}{SAT section}. \\

The special case \(k \in {1, 2} \) provides Rowley's inequalities \hyperlink{label2}{\textbf{[2]}}, \(S(n+1) \geq 4S(n)+2\) and \(S(n+2) \geq 13S(n)+8\). 
In this case, \(SE_+(2) = 4 = S(2)\) and \(SE_+(3) = 13 = S(3)\). We found other inequalities as well.

@@

\par
\hyperlink{label4}{\textbf{[4]}} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of \([\![1,197]\!]\) with  
\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only assuming \(m_5 = 67\) even after several 
weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5 seconds with the SAT solver glucose 
on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here but in the rest of this subsection, we used the parallel version of glucose). 
The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free subsets starts with a partition of 
\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among the 3 partitions of \([\![1,23]\!]\) in 
3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two different subsets. We hardcoded 
this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation time.

@@

More precisely, we verified the following results.

>>>>

@@

\begin{notation}
Let \(P\) be a predicate. We denote
\end{notation}

\par
\hyperlink{label4}{\textbf{[4]}} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of \([\![1,197]\!]\) with  
\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only assuming \(m_5 = 67\) even after several 
weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5 seconds with the SAT solver glucose 
on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here but in the rest of this subsection, we used the parallel version of glucose). 
The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free subsets starts with a partition of 
\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among the 3 partitions of \([\![1,23]\!]\) in 
3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two different subsets. We hardcoded 
this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation time. We also give the stronger 
following result.

@@

More precisely, we verified the following results (\(max~m_5\) is the greatest value of \(m_5\) for which we have not verified that \(WS(5 | m_5) \leq 196\)).
